%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Teaching/Research Assistant} % Job title
    {Colorado School of Mines} % Organization
    {Golden, Colorado} % Location
    {Aug. 2017 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item \textbf{Leadership} 
            \subitem - Introduced undergraduate students to the processes related to research, from software development to publication.
            \subitem - Fostered a collaborative research environment through the effective use of GitLab, Mendeley, Slack, and face-to-face interaction.
        \item \textbf{Teaching}
            \subitem - Supported an introductory Fortran class during lab and office hours.
            \subitem - Responsible for grading assignments in Fortran, Web Programming, and Algorithms
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Software Engineer, Professional Development Program}
    {Northrop Grumman}
    {Colorado Springs \& San Diego, USA}
    {Aug. 2015 - June 2017}
    {
      \begin{cvitems}
      \item \textbf{Embedded Software} 
          \subitem - Developed and designed the initial prototype for a cross-domain-solution on a Xilinx Ultrascale+ using NSA software guidance principles. 
          \subitem - Fostered a team-oriented development environment for new engineers in \textit{San Diego, California}, \textit{Beaver Creek, Ohio} and \textit{Orlando, Florida}. 
          \subitem - Presented technical approach to internal customers. 
        \item \textbf{Modeling \& Simulation} 
          \subitem - Developed algorithms in C\# and Java for autonomous way-point navigation in a Unity3D simulation.
          \subitem - Leveraged a novel machine learning algorithm to speed up a legacy software application by \textit{three orders} of magnitude. 
          \subitem- Presented algorithmic approach to government customers from a Department of Defense Agency.
      \end{cvitems}
    }

\end{cventries}
